---
title: "Anytime-Valid Conjoint Analysis: A Digital-Camera Case Study"
subtitle: "Supplementary case study for *Anytime-Valid Inference in Conjoint Experiments* (Molitor, Gosciak, and Lindon, 2026)"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    number_sections: true
    fig_caption: true
geometry: margin=1in
fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.align = "center")

suppressPackageStartupMessages({
  library(dplyr)
  library(ggplot2)
  library(readr)
  library(here)
})

meta <- read_csv(here("cameras_case_study", "data", "meta.csv"), show_col_types = FALSE)
final_comparison <- read_csv(here("cameras_case_study", "data", "final_comparison.csv"), show_col_types = FALSE)
sequential_estimates <- read_csv(here("cameras_case_study", "data", "sequential_av_estimates.csv"), show_col_types = FALSE)
camera_long <- read_csv(here("cameras_case_study", "data", "camera_long.csv"), show_col_types = FALSE)

term_labels <- c(
  canon     = "Canon",
  sony      = "Sony",
  nikon     = "Nikon",
  panasonic = "Panasonic",
  pixels    = "Higher pixel count",
  zoom      = "Higher zoom",
  video     = "Video capability",
  swivel    = "Swivel display",
  wifi      = "WiFi",
  price     = "Price (USD 100s)"
)
term_order <- names(term_labels)

sequential_estimates <- sequential_estimates |>
  mutate(label = factor(term_labels[term], levels = term_labels[term_order]))

final_comparison <- final_comparison |>
  mutate(
    label  = factor(term_labels[term], levels = rev(term_labels[term_order])),
    method = factor(method, levels = c("Conventional (fixed-n)", "Anytime-valid (CS)"))
  )
```

# Introduction

The parent paper establishes anytime-valid e-values and confidence sequences
(CSs) for the linear-probability ("AMCE") model of conjoint analysis, and
demonstrates their properties through simulation. This note complements those
simulations with a case study on a real conjoint dataset: a discrete-choice
survey of digital camera preferences. The goal is to show what the method
looks like end-to-end on real data -- in particular, how the confidence
sequence and e-value for each attribute effect evolve as respondents
accumulate, and how the final anytime-valid interval compares to the
conventional fixed-$n$ interval computed from the same fitted model.

All code, data, and figures for this case study live in
`cameras_case_study/` and can be regenerated with `run_all.sh`; see the
accompanying `README.md` for exact reproduction steps.

# Data

We use the `camera` dataset distributed with the R package **bayesm**
(Rossi, 2023), a panel conjoint survey of digital camera preferences from
Allenby, Brazell, Howell, and Rossi (2014a, 2014b); see also Case Study 4 in
Rossi, Allenby, and McCulloch, *Bayesian Statistics and Marketing*. The
dataset contains `r meta$G_total` respondents, each of whom completed 16
choice tasks. In every task the respondent chose among 4 camera profiles plus
an explicit outside ("none of these") option, for
`r format(meta$n_obs, big.mark = ",")` respondent-task-alternative rows in
total. Each profile is described by four mutually-exclusive brand indicators
(Canon, Sony, Nikon, Panasonic -- the outside option has all four set to
zero), five binary feature indicators (higher pixel count, higher zoom, video
capability, swivel display, WiFi), and price in hundreds of US dollars.

We treat each of the `r meta$G_total` respondents as a cluster, exactly as in
the simulations in the main paper, and fit

$$
\texttt{chosen} \sim \texttt{canon} + \texttt{sony} + \texttt{nikon} + \texttt{panasonic} +
\texttt{pixels} + \texttt{zoom} + \texttt{video} + \texttt{swivel} + \texttt{wifi} + \texttt{price}
$$

as a linear probability model via `feols()`, clustering standard errors by
respondent. Each non-intercept coefficient is an AMCE: the average marginal
effect of that attribute on the probability a profile is chosen, relative to
the outside option.

# Method

Point estimates and cluster-robust ("CRV1") standard errors come directly
from `feols()`. Anytime-valid p-values and confidence-sequence radii are then
computed from those same estimates using the e-value construction of the
parent paper, with the reference degrees of freedom and the process index
both set to $G - 1$ and $G$ respectively, where $G$ is the number of clusters
observed so far -- not the row count -- since clusters, not rows, are the
unit that accumulates sequentially here.

The tuning parameter $g$, which controls the shape of the confidence
sequence, is fixed once in advance at the value that minimizes the CS radius
at the dataset's actual final size, $G = `r meta$G_total`$ (close to the
$\sim 300$ clusters expected going in). This gives $g^\star =
`r sprintf("%.2f", meta$g_star)`$. Critically, $g^\star$ is computed once from
the planned final sample size and held fixed throughout sequential
monitoring below; re-optimizing $g$ as data accumulate would invalidate the
anytime-valid guarantee, since $g$ would then depend on how the monitoring
unfolds.

All significance levels below use $\alpha = `r meta$alpha`$.

# Results

## Confidence sequences over time

```{r fig-cs, fig.width=7, fig.height=8.5, fig.cap="Anytime-valid 95\\% confidence sequence for each AMCE as respondents accumulate. Shaded regions clipped at $\\pm 1$; very early on (roughly $G<18$) the true radius is unbounded, which is expected: a confidence sequence must sometimes be uninformative to guarantee valid coverage at every sample size, not just at a single pre-planned $n$."}
cs_cap <- 1

ggplot(
  sequential_estimates |>
    mutate(
      conf.low  = pmax(conf.low, -cs_cap),
      conf.high = pmin(conf.high, cs_cap)
    ),
  aes(x = G, y = estimate, ymin = conf.low, ymax = conf.high)
) +
  geom_ribbon(alpha = 0.25, fill = "#2C7FB8") +
  geom_line(color = "#2C7FB8", linewidth = 0.4) +
  geom_hline(yintercept = 0, linetype = "dotted", color = "grey30") +
  coord_cartesian(ylim = c(-cs_cap, cs_cap)) +
  facet_wrap(~label, ncol = 2) +
  labs(
    x = "Respondents observed (G)",
    y = "AMCE estimate, with 95% confidence sequence"
  ) +
  theme_minimal(base_size = 10) +
  theme(panel.grid.minor = element_blank(), strip.text = element_text(face = "bold"))
```

Figure \ref{fig:fig-cs} shows every attribute's confidence sequence
narrowing steadily as more respondents are observed, while remaining valid to
inspect at any point along the way -- there is no multiple-looks penalty for
having watched the price effect firm up over the first hundred or so
respondents before checking in on swivel display or WiFi.

## e-values over time

```{r fig-evalues, fig.width=7, fig.height=8.5, fig.cap="Anytime-valid e-value for each AMCE as respondents accumulate (log scale). The dashed red line is $1/\\alpha$, the threshold an e-value must cross to reject the null of no effect at level $\\alpha$; the dotted grey line is $e=1$ (neutral evidence)."}
ggplot(sequential_estimates, aes(x = G, y = e_value)) +
  geom_line(color = "#D95F02", linewidth = 0.4) +
  geom_hline(yintercept = 1 / meta$alpha, linetype = "dashed", color = "red") +
  geom_hline(yintercept = 1, linetype = "dotted", color = "grey40") +
  scale_y_log10() +
  facet_wrap(~label, ncol = 2, scales = "free_y") +
  labs(
    x = "Respondents observed (G)",
    y = "Anytime-valid e-value (log scale)"
  ) +
  theme_minimal(base_size = 10) +
  theme(panel.grid.minor = element_blank(), strip.text = element_text(face = "bold"))
```

Figure \ref{fig:fig-evalues} shows the corresponding e-value trajectories.
Every attribute's e-value exceeds the $1/\alpha$ rejection threshold by the
end of the sample, i.e. every AMCE in this study is detectably different
from zero given the full sample. The number of respondents needed to first
cross that threshold varies substantially across attributes, from 25 for
price to 110 for the weakest brand effect (Panasonic) -- under a third of
the full sample even in the slowest case. The trajectories are not always
monotonic once above the threshold (Panasonic and Sony both dip back below
it after their first crossing); this is expected of e-processes and is
harmless under the relevant decision rule, which is to stop and reject the
very first time the threshold is crossed, rather than requiring it to stay
crossed forever.

## Fixed-$n$ interval vs. confidence sequence, at the final sample size

```{r fig-final, fig.width=6.5, fig.height=4.5, fig.cap=sprintf("Final AMCE point estimate with a conventional fixed-$n$ 95\\%% confidence interval versus the anytime-valid 95\\%% confidence sequence, both computed from the same final model fit ($G = %d$).", meta$G_total)}
ggplot(
  final_comparison,
  aes(x = label, y = estimate, ymin = conf.low, ymax = conf.high, color = method)
) +
  geom_hline(yintercept = 0, linetype = "dotted", color = "grey40") +
  geom_pointrange(position = position_dodge(width = 0.5), size = 0.4) +
  coord_flip() +
  scale_color_manual(values = c(
    "Conventional (fixed-n)" = "grey40",
    "Anytime-valid (CS)"     = "#2C7FB8"
  )) +
  labs(x = NULL, y = "AMCE estimate (95% interval)", color = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", panel.grid.minor = element_blank())
```

Figure \ref{fig:fig-final} makes explicit the price of anytime validity at a
single, fixed sample size: the two methods share the same point estimate
(they are computed from the same model fit), but the confidence sequence is
visibly wider than the conventional interval for every AMCE. That extra width
is exactly what buys the ability to monitor the study continuously, as in
Figures \ref{fig:fig-cs} and \ref{fig:fig-evalues}, and still report a valid
interval or rejection decision at whatever point the analyst chooses to stop
-- something the conventional interval does not license.

# Discussion

On this real conjoint dataset, every attribute -- four camera brands, five
features, and price -- has a confidence sequence that excludes zero and an
e-value that comfortably clears the rejection threshold by the end of data
collection, and the point estimates agree with intuition (all brands and
features increase choice probability relative to the outside option; price
decreases it). The case study illustrates the two costs and benefits of the
anytime-valid approach side by side: wider intervals at any fixed sample
size, in exchange for validity at every sample size, including whichever one
an analyst actually decides to stop at.

# References

- Allenby, G., Brazell, J., Howell, J., and Rossi, P. (2014a). Economic
  Valuation of Product Features. *Quantitative Marketing and Economics*,
  12, 421-456.
- Allenby, G., Brazell, J., Howell, J., and Rossi, P. (2014b). Valuation of
  Patented Product Features. *Journal of Law and Economics*, 57, 629-663.
- Rossi, P., Allenby, G., and McCulloch, R. *Bayesian Statistics and
  Marketing*. Case Study 4.
- Rossi, P. (2023). bayesm: Bayesian Inference for Marketing/Micro-Econometrics.
  R package.
- Lindon, M., Ham, D., Tingley, M., and Bojinov, I. (2026). Anytime-valid
  linear models and regression adjusted causal inference in randomized
  experiments. *Journal of the American Statistical Association*.
  arXiv:2210.08589.
- Molitor, D., Gosciak, J., and Lindon, M. (2026). Anytime-Valid Inference in
  Conjoint Experiments.
