---
title: "Anytime-Valid Conjoint Analysis: A Candidate-Gender Case Study"
subtitle: "Supplementary case study for *Anytime-Valid Inference in Conjoint Experiments* (Molitor, Gosciak, and Lindon, 2026)"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    number_sections: true
    fig_caption: true
geometry: margin=1in
fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.align = "center")

suppressPackageStartupMessages({
  library(dplyr)
  library(ggplot2)
  library(readr)
  library(here)
  library(tibble)
})

meta <- read_csv(here("candidate_gender_case_study", "data", "meta.csv"), show_col_types = FALSE)
final_comparison <- read_csv(here("candidate_gender_case_study", "data", "final_comparison.csv"), show_col_types = FALSE)
sequential_estimates <- read_csv(here("candidate_gender_case_study", "data", "sequential_av_estimates.csv"), show_col_types = FALSE)
candidate_long <- read_csv(here("candidate_gender_case_study", "data", "candidate_long.csv"), show_col_types = FALSE)

term_labels <- c(
  orig_1ys         = "1 yr experience (ref: 0 yr)",
  orig_3ys         = "3 yr experience (ref: 0 yr)",
  orig_8ys         = "8 yr experience (ref: 0 yr)",
  orig_FM_sp       = "Spouse: farmer (ref: unmarried)",
  orig_MD_sp       = "Spouse: doctor (ref: unmarried)",
  orig_law         = "Occupation: lawyer (ref: teacher)",
  orig_may         = "Occupation: mayor (ref: teacher)",
  orig_leg         = "Occupation: legislator (ref: teacher)",
  orig_1ch         = "1 child (ref: 0)",
  orig_3ch         = "3 children (ref: 0)",
  orig_45          = "Age 45 (ref: 29)",
  orig_65          = "Age 65 (ref: 29)",
  orig_cand_female = "Candidate is female (ref: male)"
)
term_order <- names(term_labels)

sequential_estimates <- sequential_estimates |>
  mutate(label = factor(term_labels[term], levels = term_labels[term_order]))

final_comparison <- final_comparison |>
  mutate(
    label  = factor(term_labels[term], levels = rev(term_labels[term_order])),
    method = factor(method, levels = c("Conventional (fixed-n)", "Anytime-valid (CS)"))
  )
```

```{r stats, include=FALSE}
# All specific numeric claims made in the prose below are computed here,
# directly from the generated CSVs, rather than typed in by hand -- see the
# repository-wide verification discipline: never guess or assume ordering.
threshold <- 1 / meta$alpha

crossing_summary <- sequential_estimates |>
  group_by(term, label) |>
  summarize(
    first_G = if (any(e_value >= threshold)) min(G[e_value >= threshold]) else NA_real_,
    .groups = "drop"
  )

n_cross <- sum(!is.na(crossing_summary$first_G))
n_terms <- nrow(crossing_summary)

fastest_cross <- crossing_summary |> filter(!is.na(first_G)) |> slice_min(first_G, n = 1)
slowest_cross <- crossing_summary |> filter(!is.na(first_G)) |> slice_max(first_G, n = 1)
never_cross   <- crossing_summary |> filter(is.na(first_G))

female_row          <- crossing_summary |> filter(term == "orig_cand_female")
female_first_G      <- female_row$first_G
female_pct_of_sample <- 100 * female_first_G / meta$G_total
female_cross_rank    <- sum(crossing_summary$first_G <= female_first_G, na.rm = TRUE)

female_final    <- final_comparison |> filter(term == "orig_cand_female", method == "Anytime-valid (CS)")
female_est      <- female_final$estimate
female_final_e  <- sequential_estimates |> filter(term == "orig_cand_female", G == meta$G_total) |> pull(e_value)

largest_effect <- final_comparison |>
  filter(method == "Anytime-valid (CS)") |>
  slice_max(abs(estimate), n = 1)

age65_final <- sequential_estimates |> filter(term == "orig_65", G == meta$G_total)

# Of the attributes that ever cross the threshold, how many dip back below it
# at least once after their first crossing (expected, harmless e-process
# behavior under a "stop at first crossing" decision rule)?
dip_summary <- sequential_estimates |>
  semi_join(filter(crossing_summary, !is.na(first_G)), by = "term") |>
  group_by(term) |>
  arrange(G) |>
  summarize(
    fg   = min(G[e_value >= threshold]),
    dips = any(G > min(G[e_value >= threshold]) & e_value < threshold),
    .groups = "drop"
  )
n_dip <- sum(dip_summary$dips)

n_pairs <- nrow(distinct(candidate_long, responseid, contest))

inf_max_G <- sequential_estimates |>
  filter(is.infinite(conf.low) | is.infinite(conf.high)) |>
  summarize(m = max(G)) |>
  pull(m)

# Formats a large e-value as "m \times 10^{k}" for clean rendering inside
# LaTeX math mode (plain "6.8e+03" inside $...$ renders with an italicized
# "e" and spaced-out "+", which reads as a formula rather than a number).
fmt_e <- function(x) {
  expo <- floor(log10(x))
  mant <- x / 10^expo
  if (round(mant, 1) >= 10) {
    mant <- mant / 10
    expo <- expo + 1
  }
  sprintf("%.1f \\times 10^{%d}", mant, expo)
}
```

# Introduction

The parent paper establishes anytime-valid e-values and confidence sequences
(CSs) for the linear-probability ("AMCE") model of conjoint analysis, and
demonstrates their properties through simulation. This note complements
those simulations, and the companion digital-camera case study, with a case
study on a real political-science conjoint dataset: a discrete-choice survey
in which voters were shown pairs of hypothetical political candidates and
chose which one they would support. The substantive question motivating the
underlying study -- and the one this case study foregrounds -- is whether a
candidate's gender affects voter support once other biographical attributes
are held fixed. As in the companion case study, the goal is to show what the
anytime-valid method looks like end-to-end on real data: how the confidence
sequence and e-value for each candidate attribute, especially candidate
gender, evolve as respondents accumulate, and how the final anytime-valid
interval compares to the conventional fixed-$n$ interval computed from the
same fitted model.

All code, data, and figures for this case study live in
`candidate_gender_case_study/` and can be regenerated with `run_all.sh`; see
the accompanying `README.md` for exact reproduction steps.

# Data

We use the candidate-choice conjoint experiment of Teele, Kalla, and
Rosenbluth (2018), fielded to study whether social-role expectations and
traditionally-gendered biographical traits shape support for female
political candidates. Respondents were shown pairs of hypothetical candidate
biographies -- differing in years of political experience, spousal status,
occupation, number of children, age, and gender -- and asked which candidate
they would support. The outcome `winner` records whether a given candidate
profile was the one chosen in its pairwise comparison; this is the AMCE
outcome used throughout this case study, playing the same role as `chosen`
in the companion digital-camera case study. Full column definitions and
provenance are in `data/raw/data_dictionary.csv` and
`data/raw/dataverse_README.txt`.

The full replication data span both a general-population voter sample and a
sample of political elites/legislators, as well as a 2017 legislator-only
replication wave fielded with a modified attribute set. To isolate a single
clean experimental condition, comparable in spirit to the general-population
conjoint samples used elsewhere in this paper, we restrict to the original
2014 wave of the general-population voter sample under the unmodified
attribute set (`sample == "usa voter" & replication == 0`). The elite/
legislator sample and the 2017 replication are real parts of the original
study but out of scope here; see the Discussion for these as natural
extensions. After this filter, the data comprise
`r format(meta$G_total, big.mark = ",")` respondents (clusters), each
completing up to 3 candidate-comparison tasks, for
`r format(meta$n_obs, big.mark = ",")` respondent-task-candidate rows and
`r format(n_pairs, big.mark = ",")` valid pairwise comparisons in total.

Each candidate profile is described by five attributes, one-hot encoded in
the raw data with no reference level omitted: years of political experience
(0/1/3/8), spousal status (unmarried / married to a farmer / married to a
doctor), occupation (teacher / lawyer / mayor / legislator), number of
children (0/1/3), and age (29/45/65) -- plus a sixth, binary attribute, the
candidate's gender (`orig_cand_female`), which is the attribute of central
substantive interest for this case study. Because each group's dummies sum
to 1 in every row, we drop exactly one reference dummy per group before
fitting (0 years, unmarried, teacher, 0 children, age 29) to avoid perfect
collinearity with the intercept, leaving 13 non-intercept coefficients.

We treat each of the `r format(meta$G_total, big.mark = ",")` respondents as
a cluster, exactly as in the simulations in the main paper and in the
companion camera case study, and fit

$$
\begin{aligned}
\texttt{winner} \sim\ & \texttt{orig\_1ys} + \texttt{orig\_3ys} + \texttt{orig\_8ys} + \texttt{orig\_FM\_sp} + \\
& \texttt{orig\_MD\_sp} + \texttt{orig\_law} + \texttt{orig\_may} + \texttt{orig\_leg} + \\
& \texttt{orig\_1ch} + \texttt{orig\_3ch} + \texttt{orig\_45} + \texttt{orig\_65} + \texttt{orig\_cand\_female}
\end{aligned}
$$

as a linear probability model via `feols()`, clustering standard errors by
respondent (`responseid`). Each non-intercept coefficient is an AMCE: the
average marginal effect of that attribute, relative to its dropped reference
level, on the probability a candidate profile wins its pairwise comparison.

# Method

Point estimates and cluster-robust ("CRV1") standard errors come directly
from `feols()`. Anytime-valid p-values and confidence-sequence radii are then
computed from those same estimates using the e-value construction of the
parent paper, with the reference degrees of freedom and the process index
both set to $G - 1$ and $G$ respectively, where $G$ is the number of
clusters (respondents) observed so far -- not the row count -- since
clusters, not rows, are the unit that accumulates sequentially here.

The tuning parameter $g$, which controls the shape of the confidence
sequence, is fixed once in advance at the value that minimizes the CS radius
at the dataset's actual final size, $G = `r format(meta$G_total, big.mark = ",")`$.
This gives $g^\star = `r sprintf("%.2f", meta$g_star)`$. Critically,
$g^\star$ is computed once from the planned final sample size and held fixed
throughout sequential monitoring below; re-optimizing $g$ as data accumulate
would invalidate the anytime-valid guarantee, since $g$ would then depend on
how the monitoring unfolds.

All significance levels below use $\alpha = `r meta$alpha`$.

# Results

## Confidence sequences over time

```{r fig-cs, fig.width=7.5, fig.height=7.7, fig.cap=sprintf("Anytime-valid 95\\%% confidence sequence for each AMCE as respondents accumulate. Shaded regions clipped at $\\pm 1$; very early on (roughly $G<%d$) the true radius is unbounded, which is expected: a confidence sequence must sometimes be uninformative to guarantee valid coverage at every sample size, not just at a single pre-planned $n$.", inf_max_G + 1)}
cs_cap <- 1

ggplot(
  sequential_estimates |>
    mutate(
      conf.low  = pmax(conf.low, -cs_cap),
      conf.high = pmin(conf.high, cs_cap)
    ),
  aes(x = G, y = estimate, ymin = conf.low, ymax = conf.high)
) +
  geom_ribbon(alpha = 0.25, fill = "#2C7FB8") +
  geom_line(color = "#2C7FB8", linewidth = 0.4) +
  geom_hline(yintercept = 0, linetype = "dotted", color = "grey30") +
  coord_cartesian(ylim = c(-cs_cap, cs_cap)) +
  facet_wrap(~label, ncol = 3) +
  labs(
    x = "Respondents observed (G)",
    y = "AMCE estimate, with 95% confidence sequence"
  ) +
  theme_minimal(base_size = 10) +
  theme(panel.grid.minor = element_blank(), strip.text = element_text(face = "bold"))
```

Figure \ref{fig:fig-cs} shows every attribute's confidence sequence
narrowing steadily as more respondents are observed, while remaining valid to
inspect at any point along the way -- there is no multiple-looks penalty for
having watched, say, the experience effect firm up over the first few
hundred respondents before checking in on the candidate-gender effect. The
one exception is `r as.character(never_cross$label)`,
whose confidence sequence still includes zero at the full sample size
($`r sprintf("%.3f", age65_final$conf.low)`$ to
$`r sprintf("%.3f", age65_final$conf.high)`$); every other attribute's
confidence sequence excludes zero by $G = `r format(meta$G_total, big.mark = ",")`$.

## e-values over time

```{r fig-evalues, fig.width=7.5, fig.height=7.7, fig.cap="Anytime-valid e-value for each AMCE as respondents accumulate (log scale). The dashed red line is $1/\\alpha$, the threshold an e-value must cross to reject the null of no effect at level $\\alpha$; the dotted grey line is $e=1$ (neutral evidence)."}
ggplot(sequential_estimates, aes(x = G, y = e_value)) +
  geom_line(color = "#D95F02", linewidth = 0.4) +
  geom_hline(yintercept = 1 / meta$alpha, linetype = "dashed", color = "red") +
  geom_hline(yintercept = 1, linetype = "dotted", color = "grey40") +
  scale_y_log10() +
  facet_wrap(~label, ncol = 3, scales = "free_y") +
  labs(
    x = "Respondents observed (G)",
    y = "Anytime-valid e-value (log scale)"
  ) +
  theme_minimal(base_size = 10) +
  theme(panel.grid.minor = element_blank(), strip.text = element_text(face = "bold"))
```

Figure \ref{fig:fig-evalues} shows the corresponding e-value trajectories.
`r n_cross` of the `r n_terms` attributes cross the $1/\alpha$ rejection
threshold by the end of the sample; the exception is
`r as.character(never_cross$label)`, whose e-value never separates from
neutral evidence (it is $`r sprintf("%.2f", age65_final$e_value)`$ at the
final sample size), consistent with its confidence sequence including zero
throughout (Figure \ref{fig:fig-cs}). Among the `r n_cross` attributes that
do cross, the number of respondents needed to first do so varies
substantially: from $G = `r format(fastest_cross$first_G, big.mark = ",")`$
for `r as.character(fastest_cross$label)` to
$G = `r format(slowest_cross$first_G, big.mark = ",")`$ for
`r as.character(slowest_cross$label)`. Candidate gender -- the attribute of
central interest here -- first crosses at
$G = `r format(female_first_G, big.mark = ",")`$, i.e. roughly
`r sprintf("%.0f", female_pct_of_sample)`\% of the way through the sample,
making it the `r female_cross_rank`th of `r n_cross` crossing attributes to
resolve. The trajectories are not always monotonic once above the
threshold: `r n_dip` of the `r n_cross` crossing attributes, including
candidate gender, dip back below it at least once after their first
crossing. This is expected of e-processes and is harmless under the relevant
decision rule, which is to stop and reject the very first time the threshold
is crossed, rather than requiring it to stay crossed forever.

## Fixed-$n$ interval vs. confidence sequence, at the final sample size

```{r fig-final, fig.width=6.5, fig.height=5.8, fig.cap=sprintf("Final AMCE point estimate with a conventional fixed-$n$ 95\\%% confidence interval versus the anytime-valid 95\\%% confidence sequence, both computed from the same final model fit ($G = %s$).", format(meta$G_total, big.mark = ","))}
ggplot(
  final_comparison,
  aes(x = label, y = estimate, ymin = conf.low, ymax = conf.high, color = method)
) +
  geom_hline(yintercept = 0, linetype = "dotted", color = "grey40") +
  geom_pointrange(position = position_dodge(width = 0.5), size = 0.4) +
  coord_flip() +
  scale_color_manual(values = c(
    "Conventional (fixed-n)" = "grey40",
    "Anytime-valid (CS)"     = "#2C7FB8"
  )) +
  labs(x = NULL, y = "AMCE estimate (95% interval)", color = NULL) +
  theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", panel.grid.minor = element_blank())
```

Figure \ref{fig:fig-final} makes explicit the price of anytime validity at a
single, fixed sample size: the two methods share the same point estimate
(they are computed from the same model fit), but the confidence sequence is
visibly wider than the conventional interval for every AMCE. That extra
width is exactly what buys the ability to monitor the study continuously, as
in Figures \ref{fig:fig-cs} and \ref{fig:fig-evalues}, and still report a
valid interval or rejection decision at whatever point the analyst chooses
to stop -- something the conventional interval does not license. For
candidate gender specifically, both intervals exclude zero at the final
sample size, and both are centered on the same estimate,
$`r sprintf("%.3f", female_est)`$: female candidates are, if anything,
slightly more likely to win a pairwise comparison than otherwise-identical
male candidates in this sample.

# Discussion

On this real conjoint dataset, `r n_cross` of the 13 attributes -- years of
experience, spousal status, occupation, number of children, age 45 (but not
age 65), and candidate gender -- have a confidence sequence that excludes
zero and an e-value that comfortably clears the rejection threshold by the
end of data collection. As in the companion case study, the anytime-valid
approach trades away some precision at any single fixed sample size for the
ability to monitor these effects continuously and still report a valid
interval or rejection decision at whichever point an analyst actually
chooses to stop, rather than only at one pre-registered $n$.

**Candidate gender.** The coefficient on `orig_cand_female` is the attribute
of central substantive interest for this case study, since the motivating
question behind the underlying experiment is whether candidate gender
affects voter support. Its anytime-valid point estimate is
$+`r sprintf("%.3f", female_est)`$: holding experience, spousal status,
occupation, number of children, and age fixed, a female candidate is
estimated to be about `r sprintf("%.1f", 100 * female_est)` percentage
points *more* likely to win a pairwise comparison against an
otherwise-identical male candidate among 2014 general-population voters, and
this effect is anytime-valid significant
($e = `r fmt_e(female_final_e)`$ at the final
sample size). This is consistent with the original study's headline finding
of no outright hostility toward female candidates among the general
public -- if anything a modest advantage here -- rather than evidence of
straightforward voter bias against women. At the same time, the
candidate-gender effect is both comparatively small in magnitude (about
`r sprintf("%.0f", 100 * female_est / abs(largest_effect$estimate))`\% of
the size of the largest AMCE in this study,
`r as.character(largest_effect$label)`, at
$`r sprintf("%.3f", largest_effect$estimate)`$) and comparatively slow to
resolve under continuous monitoring (the
`r female_cross_rank`th of `r n_cross` attributes to cross the e-value
threshold, at `r sprintf("%.0f", female_pct_of_sample)`\% of the way through
the sample). A study designed and powered only around the large, fast-
resolving experience or occupation effects could easily be underpowered to
say anything conclusive about the smaller, slower gender effect at the same
fixed sample size -- exactly the scenario anytime-valid monitoring is
designed for, since it lets data collection continue, with a running valid
answer at every point, until whichever effect the analyst cares about has
actually resolved.

Two further caveats are worth flagging as natural extensions. First, this
case study fits a single additive AMCE model and so cannot speak to the
original study's central "double bind" finding -- that traditionally
gendered traits such as marital status, children, and occupation are
rewarded or penalized *differently* depending on candidate gender. Testing
that would require anytime-valid inference on interaction terms (e.g.
`orig_cand_female` $\times$ occupation), which the e-value and
confidence-sequence construction used here extends to directly but which we
leave to future work. Second, this case study deliberately restricts to the
2014 general-population voter sample under the original attribute set; the
2018 study also fielded a parallel sample of political elites/legislators
and a 2017 legislator-only replication with a modified attribute set, both
of which would make natural additional anytime-valid case studies,
potentially with different conclusions given that political elites and the
mass public need not react to candidate gender the same way.

# References

- Teele, D. L., Kalla, J., and Rosenbluth, F. (2018). The Ties That Double
  Bind: Social Roles and Women's Underrepresentation in Politics. *American
  Political Science Review*, 112(3), 525-541.
- Teele, D. L., Kalla, J., and Rosenbluth, F. (2018). Replication Data for:
  The Ties That Double Bind: Social Roles and Women's Underrepresentation in
  Politics. *Harvard Dataverse*. doi:10.7910/DVN/FVCGHC.
- Lindon, M., Ham, D., Tingley, M., and Bojinov, I. (2026). Anytime-valid
  linear models and regression adjusted causal inference in randomized
  experiments. *Journal of the American Statistical Association*.
  arXiv:2210.08589.
- Molitor, D., Gosciak, J., and Lindon, M. (2026). Anytime-Valid Inference in
  Conjoint Experiments.
