---
title: "Anytime-Valid Conjoint Analysis: An Immigration-Preferences Case Study"
subtitle: "Supplementary case study for *Anytime-Valid Inference in Conjoint Experiments* (Molitor, Gosciak, and Lindon, 2026)"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    number_sections: true
    fig_caption: true
geometry: margin=1in
fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.align = "center")

suppressPackageStartupMessages({
  library(cjoint)
  library(dplyr)
  library(ggplot2)
  library(knitr)
  library(readr)
  library(here)
})

meta <- read_csv(here("immigration_case_study", "data", "meta.csv"), show_col_types = FALSE)
final_comparison <- read_csv(here("immigration_case_study", "data", "final_comparison.csv"), show_col_types = FALSE)
sequential_estimates <- read_csv(here("immigration_case_study", "data", "sequential_av_estimates.csv"), show_col_types = FALSE)
immigration_long <- read_csv(here("immigration_case_study", "data", "immigration_long.csv"), show_col_types = FALSE)
```

```{r term-metadata}
# Maps every one of the ~41 non-intercept terms in final_comparison /
# sequential_estimates to its parent attribute and level, in the attributes'
# original order (Gender, Education, Language Skills, Country of Origin,
# Job, Job Experience, Job Plans, Reason for Application, Prior Entry) and,
# within an attribute, the original level order cjoint assigns (so that,
# e.g., Education levels run from "4th grade" up to "graduate degree" rather
# than alphabetically). This ordering is used for every table and figure
# below; nothing here curates *which* terms appear -- that happens later,
# only for the two "evolving over time" figures.
attr_cols <- c(
  "Gender", "Education", "Language Skills", "Country of Origin", "Job",
  "Job Experience", "Job Plans", "Reason for Application", "Prior Entry"
)
attr_prefixes <- ifelse(grepl(" ", attr_cols), paste0("`", attr_cols, "`"), attr_cols)
names(attr_prefixes) <- attr_cols

match_attr_key <- function(term) {
  hits <- attr_prefixes[vapply(attr_prefixes, function(p) startsWith(term, p), logical(1))]
  names(hits)[[which.max(nchar(hits))]]
}

data(immigrationconjoint, package = "cjoint")
level_rank_tbl <- bind_rows(lapply(attr_cols, function(a) {
  lv <- levels(immigrationconjoint[[a]])[-1] # drop the baseline level
  tibble(attribute = a, level = lv, level_rank = seq_along(lv))
}))
rm(immigrationconjoint)

cap_first <- function(x) paste0(toupper(substring(x, 1, 1)), substring(x, 2))

term_meta <- final_comparison |>
  distinct(term, statistic) |>
  mutate(
    attribute = vapply(term, match_attr_key, character(1)),
    level = substring(term, nchar(attr_prefixes[attribute]) + 1)
  ) |>
  left_join(level_rank_tbl, by = c("attribute", "level")) |>
  mutate(attribute = factor(attribute, levels = attr_cols)) |>
  arrange(attribute, level_rank) |>
  mutate(
    label = paste0(as.character(attribute), ": ", cap_first(level)),
    label = factor(label, levels = label)
  )

stopifnot(nrow(term_meta) == n_distinct(final_comparison$term), !anyNA(term_meta$level_rank))
n_terms_total <- nrow(term_meta)

# Curated subset for the two "evolving over time" figures: exactly one
# non-baseline level per attribute, chosen as the level with the largest
# |t-statistic| in the final full-sample fit (statistic is identical between
# the conventional and anytime-valid tidies, since both come from the same
# model fit -- see code/02_sequential_analysis.R).
curated <- term_meta |>
  group_by(attribute) |>
  slice_max(order_by = abs(statistic), n = 1, with_ties = FALSE) |>
  ungroup() |>
  arrange(attribute)

stopifnot(nrow(curated) == length(attr_cols), n_distinct(curated$attribute) == length(attr_cols))
curated_terms <- curated$term

curated_label_levels <- term_meta |> filter(term %in% curated_terms) |> pull(label) |> as.character()
curated <- curated |>
  mutate(
    label = factor(as.character(label), levels = curated_label_levels),
    # Two-line version ("Attribute:\nLevel") used only for facet strip
    # titles in Figures 1-2, which are narrow (3 panels across); the
    # one-line version above is used in Table 1 and is wide enough on its
    # own line there.
    facet_label = sub(": ", ":\n", as.character(label)),
    facet_label = factor(facet_label, levels = sub(": ", ":\n", curated_label_levels))
  )
```

```{r discussion-stats}
# Every number quoted in the Discussion is computed here, directly from the
# generated CSVs, rather than asserted -- see the case study's top-level
# instructions on verification discipline.
alpha <- meta$alpha
thresh <- 1 / alpha

per_term_final <- sequential_estimates |>
  group_by(term) |>
  arrange(G) |>
  summarize(
    final_G = max(G),
    final_e = e_value[which.max(G)],
    final_excludes_0 = (conf.low[which.max(G)] > 0) | (conf.high[which.max(G)] < 0),
    first_cross_G = if (any(e_value > thresh)) min(G[e_value > thresh]) else NA_integer_,
    .groups = "drop"
  ) |>
  left_join(term_meta, by = "term")

n_final_sig <- sum(per_term_final$final_excludes_0)
n_never_cross <- sum(is.na(per_term_final$first_cross_G))
n_cross_then_fall_back <- sum(!is.na(per_term_final$first_cross_G) & !per_term_final$final_excludes_0)
fall_back_terms <- per_term_final |> filter(!is.na(first_cross_G), !final_excludes_0) |> pull(label) |> as.character()

curated_final <- per_term_final |> filter(term %in% curated_terms) |> arrange(first_cross_G)
fastest <- curated_final |> slice_min(first_cross_G, n = 1, with_ties = FALSE)
slowest <- curated_final |> slice_max(first_cross_G, n = 1, with_ties = FALSE)
n_curated_dip <- sum(vapply(curated_terms, function(tm) {
  sub <- sequential_estimates |> filter(term == tm) |> arrange(G)
  fc <- min(sub$G[sub$e_value > thresh])
  any(sub$e_value[sub$G > fc] <= thresh)
}, logical(1)))

stopifnot(n_final_sig + n_never_cross + n_cross_then_fall_back == n_terms_total)

# Sign / final-estimate lookup for curated terms, used inline in the text.
# Keyed by attribute (not term), since several term strings contain literal
# backtick characters (fixest's quoting for multi-word variable names),
# which cannot appear inside an inline `r ...` code span.
final_av <- final_comparison |> filter(method == "Anytime-valid (CS)") |> select(term, estimate, conf.low, conf.high)
curated_est <- curated |> left_join(final_av, by = "term")
sign_by_attr <- setNames(
  ifelse(curated_est$estimate > 0, "positive", "negative"),
  as.character(curated_est$attribute)
)

# Smallest G at which the confidence sequence is finite for every term at
# once (nu = G - 1 alone determines this, given g fixed, so it is the same
# threshold for every term), and the largest G among the curated terms at
# which any bound still falls outside the +/-1 plotting cap used below.
finite_from_G <- sequential_estimates |>
  group_by(G) |>
  summarize(all_finite = all(is.finite(conf.low) & is.finite(conf.high)), .groups = "drop") |>
  filter(all_finite) |>
  summarize(min(G)) |>
  pull()
cs_cap <- 1
curated_beyond_cap_G <- sequential_estimates |>
  filter(term %in% curated_terms, !is.finite(conf.low) | !is.finite(conf.high) | conf.low < -cs_cap | conf.high > cs_cap) |>
  summarize(max(G)) |>
  pull()
```

# Introduction

The parent paper establishes anytime-valid e-values and confidence sequences
(CSs) for the linear-probability ("AMCE") model of conjoint analysis, and
demonstrates their properties through simulation. A companion case study
(`cameras_case_study/`) applies the method to a digital-camera conjoint
dataset. This note provides a second, independent real-data case study,
using the immigration-preferences conjoint experiment of Hainmueller,
Hopkins, and Yamamoto (2014) -- the paper that originally introduced the
AMCE (average marginal component effect) estimator itself, the very estimand
the parent paper's anytime-valid machinery is built to test sequentially.
Using their data is thus an especially direct fit for this method: it lets
us trace anytime-valid evidence through time on the same dataset, and the
same estimand, that motivated the AMCE framework in the first place.

As in the camera case study, the goal here is to show what the method looks
like end-to-end on real data -- how the confidence sequence and e-value for
each attribute effect evolve as respondents accumulate, and how the final
anytime-valid interval compares to the conventional fixed-$n$ interval
computed from the same fitted model. This dataset is also a useful stress
test for the method along a different axis than the camera study: its nine
conjoint attributes are all multi-level categorical factors rather than
simple binary indicators, producing `r n_terms_total` non-baseline AMCE
coefficients instead of ten.

All code, data, and figures for this case study live in
`immigration_case_study/` and can be regenerated with `run_all.sh`; see the
accompanying `README.md` for exact reproduction steps.

# Data

We use the `immigrationconjoint` dataset distributed with the R package
**cjoint** (Barari, Berwick, Hainmueller, Hopkins, Liu, Strezhnev, and
Yamamoto), from the conjoint survey fielded by Hainmueller, Hopkins, and
Yamamoto (2014). A nationally representative sample of
`r format(meta$G_total, big.mark = ",")` American adults each completed 5
choice tasks; in each task the respondent
saw two hypothetical immigrant profiles side by side and chose which one
should be admitted to the United States (unlike the camera study, there is
no explicit outside/"neither" option -- every task forces a choice between
the two profiles shown). This gives `r format(meta$n_obs, big.mark = ",")`
respondent-task-profile rows in total, one per profile shown. The data are
distributed already in this long format, so no reshaping is required.

Each profile is described by nine attributes, every one a multi-level
categorical factor: `Gender`, `Education`, `Language Skills`,
`Country of Origin`, `Job`, `Job Experience`, `Job Plans`,
`Reason for Application`, and `Prior Entry`. Two respondent-level columns
(`ethnocentrism`) and two pre-computed helper columns (`LangPos`,
`PriorPos`) are not used as regressors. We treat each of the
`r format(meta$G_total, big.mark = ",")` respondents as a cluster, exactly as in the camera study
and the simulations in the main paper, and fit

$$
\begin{aligned}
\texttt{Chosen\_Immigrant} \sim\ & \texttt{Gender} + \texttt{Education} + \texttt{Language Skills} + \texttt{Country of Origin} + \texttt{Job}\ + \\
& + \texttt{Job Experience} + \texttt{Job Plans} + \texttt{Reason for Application} + \texttt{Prior Entry}
\end{aligned}
$$

as a linear probability model via `feols()`, clustering standard errors by
respondent. This is `cjoint`'s own documented formula for this dataset (see
`?cjoint::immigrationconjoint`), used verbatim. Each non-intercept
coefficient is an AMCE: the average marginal effect of that attribute level
on the probability a profile is chosen, relative to a reference level for
that attribute (e.g. India for country of origin, janitor for job, no formal
schooling for education) -- the same reference levels used throughout
Hainmueller, Hopkins, and Yamamoto (2014). Because plain-text CSV storage
does not preserve factor level order, `code/02_sequential_analysis.R`
explicitly restores these reference levels from the `cjoint` package before
fitting any model, rather than letting them default to whatever level sorts
first alphabetically.

# Method

Point estimates and cluster-robust ("CRV1") standard errors come directly
from `feols()`. Anytime-valid p-values and confidence-sequence radii are
then computed from those same estimates using the e-value construction of
the parent paper, with the reference degrees of freedom and the process
index both set to $G - 1$ and $G$ respectively, where $G$ is the number of
respondents (clusters) observed so far -- not the row count -- since
clusters, not rows, are the unit that accumulates sequentially here.

The tuning parameter $g$, which controls the shape of the confidence
sequence, is fixed once in advance at the value that minimizes the CS radius
at the dataset's actual final size, $G = `r meta$G_total`$ respondents. This
gives $g^\star = `r sprintf("%.2f", meta$g_star)`$. As in the camera study,
$g^\star$ is computed once from the planned final sample size and held fixed
throughout sequential monitoring below; re-optimizing $g$ as data accumulate
would invalidate the anytime-valid guarantee, since $g$ would then depend on
how the monitoring unfolds. All significance levels below use
$\alpha = `r meta$alpha`$.

Fitting all nine attributes as multi-level factors produces
`r n_terms_total` non-baseline dummy coefficients -- far more than the
camera study's 10 binary attributes. `data/final_comparison.csv` and
`data/sequential_av_estimates.csv` contain **all** `r n_terms_total` of
them; no coefficient is dropped from the underlying results. For the two
figures that trace evidence *over time* (Figures \ref{fig:fig-cs} and
\ref{fig:fig-evalues}), however, faceting all `r n_terms_total` coefficients
into small multiples would be unreadable. We instead curate exactly one
representative non-baseline level per attribute -- nine terms, comparable in
number to the camera study's ten-panel grid -- selected by an objective
rule: **the non-baseline level with the largest absolute $t$-statistic in
the final full-sample fit, per attribute**. Table \ref{tab:curated-table}
shows the resulting selection. The complete `r n_terms_total`-coefficient
results, curated or not, remain available in `data/final_comparison.csv`
and are shown in full in Figure \ref{fig:fig-final}.

```{r curated-table}
curated |>
  transmute(
    Attribute = as.character(attribute),
    `Selected level` = cap_first(level),
    `t-statistic` = round(statistic, 2)
  ) |>
  kable(
    caption = sprintf("\\label{tab:curated-table}Curated one-per-attribute selection used in Figures 1 and 2: for each attribute, the non-baseline level with the largest |t-statistic| in the final full-sample fit ($G = %d$).", meta$G_total)
  )
```

# Results

## Confidence sequences over time

```{r fig-cs, fig.width=7, fig.height=7.5, fig.cap=sprintf("Anytime-valid 95\\%% confidence sequence for the curated one-per-attribute AMCE (Table \\ref{tab:curated-table}) as respondents accumulate. Shaded regions clipped at $\\pm 1$; very early on (roughly $G<%d$) the confidence sequence is either unbounded ($G \\le %d$, where $\\nu=G-1$ is too small to be informative) or wider than the plotted range. This is expected: a confidence sequence must sometimes be uninformative to guarantee valid coverage at every sample size, not just at a single pre-planned $n$.", curated_beyond_cap_G + 1, finite_from_G - 1)}
cs_plot_data <- sequential_estimates |>
  filter(term %in% curated_terms) |>
  left_join(curated |> select(term, facet_label), by = "term") |>
  mutate(
    conf.low  = pmax(conf.low, -cs_cap),
    conf.high = pmin(conf.high, cs_cap)
  )

ggplot(cs_plot_data, aes(x = G, y = estimate, ymin = conf.low, ymax = conf.high)) +
  geom_ribbon(alpha = 0.25, fill = "#2C7FB8") +
  geom_line(color = "#2C7FB8", linewidth = 0.4) +
  geom_hline(yintercept = 0, linetype = "dotted", color = "grey30") +
  coord_cartesian(ylim = c(-cs_cap, cs_cap)) +
  facet_wrap(~facet_label, ncol = 3) +
  labs(
    x = "Respondents observed (G)",
    y = "AMCE estimate, with 95% confidence sequence"
  ) +
  theme_minimal(base_size = 10) +
  theme(panel.grid.minor = element_blank(), strip.text = element_text(face = "bold", size = 7.5, lineheight = 0.9))
```

Figure \ref{fig:fig-cs} shows each curated attribute's confidence sequence
narrowing steadily as more respondents are observed, while remaining valid
to inspect at any point along the way -- there is no multiple-looks penalty
for having watched, say, the education effect firm up over the first hundred
or so respondents before checking in on gender or reason for application
much later.

## e-values over time

```{r fig-evalues, fig.width=7, fig.height=7.5, fig.cap="Anytime-valid e-value for the curated one-per-attribute AMCE (Table \\ref{tab:curated-table}) as respondents accumulate (log scale). The dashed red line is $1/\\alpha$, the threshold an e-value must cross to reject the null of no effect at level $\\alpha$; the dotted grey line is $e=1$ (neutral evidence)."}
ev_plot_data <- sequential_estimates |>
  filter(term %in% curated_terms) |>
  left_join(curated |> select(term, facet_label), by = "term")

ggplot(ev_plot_data, aes(x = G, y = e_value)) +
  geom_line(color = "#D95F02", linewidth = 0.4) +
  geom_hline(yintercept = 1 / meta$alpha, linetype = "dashed", color = "red") +
  geom_hline(yintercept = 1, linetype = "dotted", color = "grey40") +
  scale_y_log10() +
  facet_wrap(~facet_label, ncol = 3, scales = "free_y") +
  labs(
    x = "Respondents observed (G)",
    y = "Anytime-valid e-value (log scale)"
  ) +
  theme_minimal(base_size = 10) +
  theme(panel.grid.minor = element_blank(), strip.text = element_text(face = "bold", size = 7.5, lineheight = 0.9))
```

Figure \ref{fig:fig-evalues} shows the corresponding e-value trajectories.
All nine curated attributes exceed the $1/\alpha$ rejection threshold at
some point before the full sample is reached, but the number of respondents
needed to first do so varies enormously: from $G = `r fastest$first_cross_G`$
for `r as.character(fastest$label)` to $G = `r slowest$first_cross_G`$ for
`r as.character(slowest$label)` -- barely `r meta$G_total - slowest$first_cross_G`
respondents short of the full sample, and only marginally so (its e-value
dips back under the threshold at least once more before the study ends).
More generally, `r n_curated_dip` of the 9 curated trajectories dip back
below the threshold at least once after their first crossing; this is
expected of e-processes and is harmless under the relevant decision rule,
which is to stop and reject the very first time the threshold is crossed,
rather than requiring it to stay crossed forever.

## Fixed-$n$ interval vs. confidence sequence, at the final sample size

```{r fig-final, fig.width=7.5, fig.height=8.2, fig.cap=sprintf("Final AMCE point estimate with a conventional fixed-$n$ 95\\%% confidence interval versus the anytime-valid 95\\%% confidence sequence, for all %d non-baseline coefficients, both computed from the same final model fit ($G = %d$). Attributes are grouped in the order introduced in the Data section; levels within an attribute follow their original order in the source data.", n_terms_total, meta$G_total)}
final_plot_data <- final_comparison |>
  left_join(term_meta |> select(term, label), by = "term") |>
  mutate(
    label = factor(as.character(label), levels = rev(levels(term_meta$label))),
    method = factor(method, levels = c("Conventional (fixed-n)", "Anytime-valid (CS)"))
  )

ggplot(
  final_plot_data,
  aes(x = label, y = estimate, ymin = conf.low, ymax = conf.high, color = method)
) +
  geom_hline(yintercept = 0, linetype = "dotted", color = "grey40") +
  geom_pointrange(position = position_dodge(width = 0.6), size = 0.25, linewidth = 0.4) +
  coord_flip() +
  scale_color_manual(values = c(
    "Conventional (fixed-n)" = "grey40",
    "Anytime-valid (CS)"     = "#2C7FB8"
  )) +
  labs(x = NULL, y = "AMCE estimate (95% interval)", color = NULL) +
  theme_minimal(base_size = 9) +
  theme(legend.position = "bottom", panel.grid.minor = element_blank())
```

Figure \ref{fig:fig-final} makes explicit the price of anytime validity at a
single, fixed sample size, across the complete set of `r n_terms_total`
coefficients: the two methods share the same point estimate in every case
(they are computed from the same model fit), but the confidence sequence is
visibly wider than the conventional interval for every coefficient. That
extra width is exactly what buys the ability to monitor the study
continuously, as in Figures \ref{fig:fig-cs} and \ref{fig:fig-evalues}, and
still report a valid interval or rejection decision at whatever point the
analyst chooses to stop -- something the conventional interval does not
license. The figure also makes clear that not every coefficient's interval
excludes zero at the final sample size: of the `r n_terms_total`
non-baseline levels, `r n_final_sig` have a 95% confidence sequence
(equivalently, an e-value) that excludes zero (exceeds $1/\alpha$) at
$G = `r meta$G_total`$, and `r n_terms_total - n_final_sig` do not.

# Discussion

Unlike the camera study, where every attribute's effect was eventually
detectable, here the picture is more mixed -- itself a realistic feature of
this dataset, not an artifact of the anytime-valid method: of the
`r n_terms_total` non-baseline AMCEs, `r n_final_sig` have anytime-valid
evidence against the null of no effect by the end of data collection, while
`r n_never_cross` never cross the rejection threshold at any point during
the study, mostly specific `Job` categories (relative to janitor) and
`Country of Origin` levels (relative to India) whose effects on admission
preferences are small and not detectable at this sample size. A further
`r n_cross_then_fall_back` -- `r paste(fall_back_terms, collapse = ", ")` --
cross the threshold at some point but fall back below it by the final
sample; notably, all three are `Country of Origin` levels. This is exactly
the scenario the "stop at first crossing" decision rule is designed for: an
analyst monitoring any of these three attributes anytime-validly would have
correctly rejected the null when the e-value first crossed the threshold,
even though a fixed-$n$ analysis run only once, at the final sample, would
have missed that evidence entirely.

Among the nine curated, one-per-attribute AMCEs, the point estimates agree
with the qualitative pattern in Hainmueller, Hopkins, and Yamamoto (2014):
having a college degree (`r sign_by_attr[["Education"]]`), more job
experience (`r sign_by_attr[["Job Experience"]]`), and a high-status job
like doctor (`r sign_by_attr[["Job"]]`) all raise the chance a profile is
chosen, while needing an interpreter to speak English
(`r sign_by_attr[["Language Skills"]]`), having no plans to look
for work (`r sign_by_attr[["Job Plans"]]`), a prior
unauthorized entry (`r sign_by_attr[["Prior Entry"]]`),
coming from Iraq rather than India (`r sign_by_attr[["Country of Origin"]]`),
applying to seek a better job rather than reunite with family
(`r sign_by_attr[["Reason for Application"]]`), and being male
rather than female (`r sign_by_attr[["Gender"]]`) all lower it. As in the
camera study, the case study illustrates the two costs and benefits of the
anytime-valid approach side by side: wider intervals at any fixed sample
size, in exchange for validity at every sample size -- including whichever
one an analyst actually decides to stop at, and including attributes, like
several of the `Country of Origin` levels here, whose evidence appears only
transiently along the way.

# References

- Hainmueller, J., Hopkins, D., and Yamamoto, T. (2014). Causal Inference in
  Conjoint Analysis: Understanding Multi-Dimensional Choices via Stated
  Preference Experiments. *Political Analysis*, 22(1), 1-30.
- Barari, S., Berwick, E., Hainmueller, J., Hopkins, D., Liu, S., Strezhnev,
  A., and Yamamoto, T. (2026). cjoint: AMCE Estimator for Conjoint
  Experiments. R package version 2.1.3.
- Lindon, M., Ham, D., Tingley, M., and Bojinov, I. (2026). Anytime-valid
  linear models and regression adjusted causal inference in randomized
  experiments. *Journal of the American Statistical Association*.
  arXiv:2210.08589.
- Molitor, D., Gosciak, J., and Lindon, M. (2026). Anytime-Valid Inference in
  Conjoint Experiments.
