---
title: "Anytime-Valid Conjoint Analysis: A European Asylum-Seeker Case Study"
subtitle: "Supplementary case study for *Anytime-Valid Inference in Conjoint Experiments* (Molitor, Gosciak, and Lindon, 2026)"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    number_sections: true
    fig_caption: true
geometry: margin=1in
fontsize: 11pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.align = "center")

suppressPackageStartupMessages({
  library(dplyr)
  library(tidyr)
  library(ggplot2)
  library(readr)
  library(here)
  library(knitr)
})

meta <- read_csv(here("asylum_case_study", "data", "meta.csv"), show_col_types = FALSE)
final_comparison <- read_csv(here("asylum_case_study", "data", "final_comparison.csv"), show_col_types = FALSE)
sequential_estimates <- read_csv(here("asylum_case_study", "data", "sequential_av_estimates.csv"), show_col_types = FALSE)

alpha <- meta$alpha
threshold <- 1 / alpha

## ---- Attribute bookkeeping -------------------------------------------------

attribute_display <- c(
  cconsist  = "Testimony consistency",
  cgender   = "Gender",
  corigin   = "Country of origin",
  cage      = "Age",
  cjob      = "Previous occupation",
  cvulner   = "Vulnerability",
  creason   = "Reason for migrating",
  creligion = "Religion",
  clang     = "Language skills"
)
attribute_vars <- names(attribute_display)

# Alphabetically-first level per attribute -- R's default factor() ordering,
# used (and independently verified against the raw data) as the reference
# level for every attribute below.
baseline_level <- c(
  cconsist  = "Major inconsistencies",
  cgender   = "Female",
  corigin   = "Afghanistan",
  cage      = "21 Years",
  cjob      = "Accountant",
  cvulner   = "Handicapped",
  creason   = "Economic opportunities",
  creligion = "Agnostic",
  clang     = "Broken"
)

term_attribute <- function(term) {
  attribute_vars[vapply(attribute_vars, function(a) startsWith(term, a), logical(1))][1]
}

all_terms <- final_comparison |> distinct(term) |> pull(term)
term_attr_map <- vapply(all_terms, term_attribute, character(1))
term_level_map <- substring(all_terms, nchar(term_attr_map) + 1)
term_labels <- setNames(paste0(attribute_display[term_attr_map], ": ", term_level_map), all_terms)
term_order <- all_terms

stopifnot(length(all_terms) == 27, !anyNA(term_attr_map))

sequential_estimates <- sequential_estimates |>
  mutate(label = factor(term_labels[term], levels = term_labels[term_order]))

final_comparison <- final_comparison |>
  mutate(
    label  = factor(term_labels[term], levels = rev(term_labels[term_order])),
    method = factor(method, levels = c("Conventional (fixed-n)", "Anytime-valid (CS)"))
  )

# Reference table of attributes and levels for the Data section.
attribute_table <- tibble(attribute = attribute_vars) |>
  rowwise() |>
  mutate(
    Variable = attribute,
    Attribute = attribute_display[[attribute]],
    Levels = paste0(
      baseline_level[[attribute]], " (baseline), ",
      paste(term_level_map[term_attr_map == attribute], collapse = ", ")
    )
  ) |>
  ungroup() |>
  select(Variable, Attribute, Levels)

## ---- Curated 9: one coefficient per attribute, for the two over-time figures
## Rule: within each attribute, the non-baseline level with the largest |t|
## statistic in the FINAL full-sample fit. sequential_estimates at G == max(G)
## is exactly that final full-sample fit, since G_total is always included in
## the sequential grid (see 02_sequential_analysis.R).

final_fit_stats <- sequential_estimates |>
  filter(G == max(G)) |>
  mutate(attribute = vapply(term, term_attribute, character(1)))
stopifnot(max(final_fit_stats$G) == meta$G_total, nrow(final_fit_stats) == length(all_terms))

curated <- final_fit_stats |>
  group_by(attribute) |>
  slice_max(abs(statistic), n = 1, with_ties = FALSE) |>
  ungroup() |>
  mutate(attribute_label = attribute_display[attribute]) |>
  arrange(match(attribute, attribute_vars))

curated_terms <- curated$term
stopifnot(
  length(curated_terms) == length(attribute_vars),
  length(unique(curated_terms)) == length(attribute_vars)
)

sequential_curated <- sequential_estimates |> filter(term %in% curated_terms)

curated_table <- curated |>
  transmute(
    Attribute = attribute_label,
    Level = term_level_map[match(term, all_terms)],
    Estimate = sprintf("%.3f", estimate),
    `t statistic` = sprintf("%.1f", statistic)
  )

## ---- Verified facts used in the prose below --------------------------------
## (Computed here from the generated CSVs and never hand-typed, per this
## paper's verification policy for real-data case studies: every specific
## numeric claim below is checked against actual output, and several are
## additionally guarded by stopifnot() so the report fails to render, rather
## than silently stating something false, if the underlying data changes.)

# First G at which each curated term's e-value crosses 1/alpha.
G_cross_curated <- vapply(curated_terms, function(tm) {
  sub <- sequential_curated[sequential_curated$term == tm, ]
  min(sub$G[sub$e_value >= threshold])
}, numeric(1))
names(G_cross_curated) <- curated_terms
stopifnot(all(is.finite(G_cross_curated))) # every curated term crosses eventually

fastest_term <- names(which.min(G_cross_curated))
slowest_term <- names(which.max(G_cross_curated))

# Non-monotonicity: does e_value dip back below the threshold after its first
# crossing, for any curated term?
nonmonotonic_curated <- curated_terms[vapply(curated_terms, function(tm) {
  sub <- sequential_curated[sequential_curated$term == tm, ]
  gc <- G_cross_curated[[tm]]
  any(sub$e_value[sub$G >= gc] < threshold)
}, logical(1))]

# CS finiteness: t_radius() depends only on (g*, G, alpha), not on the
# coefficient's own estimate/SE, so every one of the 27 coefficients' bounds
# should become (and remain) finite at exactly the same G.
finite_mask <- is.finite(sequential_estimates$conf.low) & is.finite(sequential_estimates$conf.high)
finiteness_onset <- min(sequential_estimates$G[finite_mask])
stopifnot(
  all(sequential_estimates$G[!finite_mask] < finiteness_onset),
  all(finite_mask[sequential_estimates$G >= finiteness_onset])
)

# Ribbon cap for Figure 1: chosen larger than every finite bound observed
# among the curated terms, so the cap only ever clips genuinely-infinite
# early bounds, never a legitimate finite one.
cs_cap <- 0.6
widest_finite <- max(
  abs(sequential_curated$conf.low[is.finite(sequential_curated$conf.low)]),
  abs(sequential_curated$conf.high[is.finite(sequential_curated$conf.high)])
)
stopifnot(widest_finite <= cs_cap)

# e-value cap for Figure 2: some e-values overflow double-precision floating
# point (become literally Inf) for very large final test statistics. Exactly
# one curated term does this, and only in the last portion of the range. The
# cap (e_cap) is chosen above every finite value reached by the *other* eight
# curated terms, so it only ever affects that one term's tail.
curated_inf_terms <- sequential_curated |> filter(is.infinite(e_value)) |> distinct(term) |> pull(term)
stopifnot(length(curated_inf_terms) == 1, curated_inf_terms == curated$term[curated$attribute == "creason"])
e_overflow_term <- curated_inf_terms
e_overflow_label <- term_labels[[e_overflow_term]]
e_cap <- 1e300

other_curated_max_finite <- max(sequential_curated$e_value[
  is.finite(sequential_curated$e_value) & sequential_curated$term != e_overflow_term
])
stopifnot(other_curated_max_finite < e_cap)

# First G at which the *displayed* (capped) line for e_overflow_term departs
# from its true value, i.e. first reaches the cap; and, separately, the
# (later) G at which it becomes literally infinite in double precision.
e_overflow_onset <- sequential_curated |>
  filter(term == e_overflow_term, e_value >= e_cap) |>
  summarize(g = min(G)) |>
  pull(g)
e_overflow_inf_onset <- sequential_curated |>
  filter(term == e_overflow_term, is.infinite(e_value)) |>
  summarize(g = min(G)) |>
  pull(g)
stopifnot(e_overflow_onset <= e_overflow_inf_onset)

# Final-sample significance comparison across all 27 AMCEs: conventional
# fixed-n vs. anytime-valid, both read off the same final model fit.
sig_status <- final_comparison |> mutate(excludes_zero = conf.low > 0 | conf.high < 0)
conv_sig <- sig_status |> filter(method == "Conventional (fixed-n)") |> select(term, conv_sig = excludes_zero)
av_sig   <- sig_status |> filter(method == "Anytime-valid (CS)")     |> select(term, av_sig = excludes_zero)
final_wide <- inner_join(conv_sig, av_sig, by = "term")
stopifnot(nrow(final_wide) == length(all_terms))

n_both_sig    <- sum(final_wide$conv_sig & final_wide$av_sig)
n_conv_only   <- sum(final_wide$conv_sig & !final_wide$av_sig)
n_av_only     <- sum(!final_wide$conv_sig & final_wide$av_sig)
n_neither_sig <- sum(!final_wide$conv_sig & !final_wide$av_sig)
stopifnot(n_both_sig + n_conv_only + n_av_only + n_neither_sig == length(all_terms))

conv_only_terms <- final_wide$term[final_wide$conv_sig & !final_wide$av_sig]
neither_terms   <- final_wide$term[!final_wide$conv_sig & !final_wide$av_sig]
conv_only_labels_text <- paste(term_labels[conv_only_terms], collapse = "; ")
neither_labels_text   <- paste(term_labels[neither_terms], collapse = "; ")

# Among the conv-only terms, which ones' e-value *ever* crossed the threshold
# at some earlier G before falling back below it by the final sample?
conv_only_ever_crossed <- conv_only_terms[vapply(conv_only_terms, function(tm) {
  any(sequential_estimates$e_value[sequential_estimates$term == tm] >= threshold)
}, logical(1))]
conv_only_never_crossed <- setdiff(conv_only_terms, conv_only_ever_crossed)
```

# Introduction

The parent paper establishes anytime-valid e-values and confidence sequences
(CSs) for the linear-probability ("AMCE") model of conjoint analysis, and
demonstrates their properties through simulation. This note is a second
real-data case study, complementing the digital-camera case study with a
large-scale political-science conjoint experiment: a forced-choice survey of
European attitudes toward asylum seekers. Relative to the camera study (332
respondents, 10 AMCEs from mostly binary attributes), this dataset is a
stress test of scale and complexity -- `r format(meta$G_total, big.mark = ",")`
respondents and nine multi-level categorical attributes, producing
`r length(all_terms)` AMCEs -- and it surfaces real features that the smaller
camera dataset did not: some coefficients' e-values grow large enough to
overflow floating point, not every AMCE ends up distinguishable from zero
even at the full sample, and the conventional and anytime-valid conclusions
concretely disagree for a handful of attribute levels. All of these are
reported below exactly as found, verified directly against the generated
data rather than assumed.

All code, data, and figures for this case study live in
`asylum_case_study/` and can be regenerated with `run_all.sh`; see the
accompanying `README.md` for exact reproduction steps.

# Data

We use the 2016 wave of the conjoint experiment from Bansak, Hainmueller, and
Hangartner (2016), fielded across 15 European countries. Respondents were
shown pairs of hypothetical asylum-seeker profiles and, in each of 5 tasks,
forced to choose which of the two profiles they would prefer to see admitted.
Each profile was described by nine randomized attributes. The specific CSV
analyzed here was released as part of the replication archive for a related
follow-up study, Bansak, Hainmueller, and Hangartner (2023), via Harvard
Dataverse (see References); that archive is the provenance of this file, while
the study design and this wave of data originate in the 2016 paper.

The raw file contains 180,300 rows (18,030 respondents $\times$ 5 tasks
$\times$ 2 profiles). Nine respondents (90 rows) have every one of the nine
attribute columns missing -- corrupted, incomplete records -- and are dropped;
no other rows have any missing attribute. After cleaning,
`r format(meta$G_total, big.mark = ",")` respondents remain, contributing
`r format(meta$n_obs, big.mark = ",")` rows in total (10 rows per respondent:
5 tasks $\times$ 2 profiles), with every respondent's rows verified to be
complete and every task a genuine forced choice (exactly one of the two
profiles preferred). We treat each respondent as a cluster, exactly as in the
simulations in the main paper and in the camera case study.

The nine attributes, converted to factors before fitting, are:

```{r attribute-table, results='asis'}
cat(paste0(
  "- **", attribute_table$Attribute, "** (`", attribute_table$Variable, "`): ",
  attribute_table$Levels
), sep = "\n")
```

The first-listed (alphabetically first) level of each attribute is the
reference level against which its AMCEs are measured, R's default `factor()`
convention. We fit

$$
\texttt{pref} \sim \texttt{cconsist}+\texttt{cgender}+\texttt{corigin}+\texttt{cage}+\texttt{cjob}+\texttt{cvulner}+\texttt{creason}+\texttt{creligion}+\texttt{clang}
$$

as a linear probability model via `feols()`, clustering standard errors by
respondent (`ResponseId`). Each of the `r length(all_terms)` non-intercept
coefficients is an AMCE: the average marginal effect of that attribute level,
relative to its attribute's baseline, on the probability a profile is
preferred.

# Method

Point estimates and cluster-robust ("CRV1") standard errors come directly
from `feols()`. Anytime-valid p-values and confidence-sequence radii are then
computed from those same estimates using the e-value construction of the
parent paper, with the reference degrees of freedom and the process index
both set to $G - 1$ and $G$ respectively, where $G$ is the number of clusters
(respondents) observed so far -- not the row count -- since clusters, not
rows, are the unit that accumulates sequentially here.

The tuning parameter $g$, which controls the shape of the confidence
sequence, is fixed once in advance at the value that minimizes the CS radius
at the dataset's actual final size, $G = `r format(meta$G_total, big.mark=",")`$.
This gives $g^\star = `r sprintf("%.2f", meta$g_star)`$. Critically,
$g^\star$ is computed once from the final sample size and held fixed
throughout sequential monitoring below; re-optimizing $g$ as data accumulate
would invalidate the anytime-valid guarantee, since $g$ would then depend on
how the monitoring unfolds. All significance levels below use
$\alpha = `r meta$alpha`$, so the e-value rejection threshold is
$1/\alpha = `r threshold`$.

Refitting at every single respondent, as the smaller camera case study does,
is unnecessary here and costly at this scale: with
`r format(meta$G_total, big.mark=",")` respondents that would mean roughly
that many `feols()` calls plus as many `dplyr::filter()` passes over a
180,000-row frame. A short timing test (fits spread across the full range of
$G$, including the filtering step) measured roughly 0.02-0.13 seconds per
fit, growing mildly with $G$. We therefore step the sequential refit by 100
respondents, giving `r meta$n_fits` total fits from $G=5$ up to
$G = `r format(meta$G_total, big.mark=",")`$ (the final value is always
included, so the last sequential fit exactly reproduces the final fit below)
-- comfortably within the targeted 150-400 refits, and measured at
`r sprintf("%.0f", meta$elapsed_sec)` seconds of actual runtime, well inside
a 3-minute budget.

With `r length(all_terms)` non-baseline coefficients across nine attributes,
faceting every coefficient in the two over-time figures below (confidence
sequences and e-values, Figures \ref{fig:fig-cs} and \ref{fig:fig-evalues})
would be unreadable. For those two figures only, we curate exactly one
representative coefficient per attribute, chosen by an objective, pre-specifiable
rule: **the non-baseline level with the largest $|t|$ statistic in the final
full-sample fit, within each attribute**. All `r length(all_terms)`
non-intercept coefficients are retained in the underlying data
(`final_comparison.csv`, `sequential_av_estimates.csv`) and in Figure
\ref{fig:fig-final}; only Figures \ref{fig:fig-cs} and \ref{fig:fig-evalues}
are curated for readability. The nine coefficients this rule selects are:

```{r curated-table}
kable(curated_table, align = c("l", "l", "r", "r"))
```

# Results

## Confidence sequences over time

```{r fig-cs, fig.width=7, fig.height=7.3, fig.cap=sprintf("Anytime-valid 95\\%% confidence sequence for the nine curated AMCEs (one per attribute; see Method) as respondents accumulate. Shaded regions are clipped at $\\pm%.1f$, which is wider than every finite bound in the data (the widest is %.3f in absolute value) -- so the clip affects only genuinely-infinite early bounds, never a legitimate finite one. Below $G=%d$, the confidence-sequence radius is infinite for \\textit{every} one of the %d coefficients in this dataset, curated or not, since the radius depends only on $G$, $g^\\star$, and $\\alpha$ -- not on the coefficient's own estimate -- and is expected: a confidence sequence must sometimes be uninformative to guarantee valid coverage at every sample size, not just a single pre-planned $n$.", cs_cap, widest_finite, finiteness_onset, length(all_terms))}
ggplot(
  sequential_curated |>
    mutate(
      conf.low  = pmax(conf.low, -cs_cap),
      conf.high = pmin(conf.high, cs_cap)
    ),
  aes(x = G, y = estimate, ymin = conf.low, ymax = conf.high)
) +
  geom_ribbon(alpha = 0.25, fill = "#2C7FB8") +
  geom_line(color = "#2C7FB8", linewidth = 0.4) +
  geom_hline(yintercept = 0, linetype = "dotted", color = "grey30") +
  coord_cartesian(ylim = c(-cs_cap, cs_cap)) +
  facet_wrap(~label, ncol = 2) +
  labs(
    x = "Respondents observed (G)",
    y = "AMCE estimate, with 95% confidence sequence"
  ) +
  theme_minimal(base_size = 10) +
  theme(panel.grid.minor = element_blank(), strip.text = element_text(face = "bold"))
```

Figure \ref{fig:fig-cs} shows each curated attribute's confidence sequence
narrowing steadily as more respondents are observed, while remaining valid to
inspect at any point along the way -- there is no multiple-looks penalty for
having watched, say, testimony consistency firm up over the first thousand or
so respondents before checking in on country of origin or religion.

## e-values over time

```{r fig-evalues, fig.width=7, fig.height=7.3, fig.cap=sprintf("Anytime-valid e-value for the same nine curated AMCEs as respondents accumulate (log scale). The dashed red line is $1/\\alpha=%d$, the threshold an e-value must cross to reject the null of no effect at level $\\alpha$; the dotted grey line is $e=1$ (neutral evidence). e-values are capped at $10^{300}$ for display, which affects only %s: from $G=%s$ its true e-value exceeds $10^{300}$, and from $G=%s$ onward it exceeds the range representable in double-precision floating point altogether (i.e., is exactly infinite); both are shown at the display cap. The underlying CSV retains the true, uncapped ($\\infty$) values throughout.", threshold, e_overflow_label, format(e_overflow_onset, big.mark=","), format(e_overflow_inf_onset, big.mark=","))}
ggplot(
  sequential_curated |> mutate(e_value = pmin(e_value, e_cap)),
  aes(x = G, y = e_value)
) +
  geom_line(color = "#D95F02", linewidth = 0.4) +
  geom_hline(yintercept = threshold, linetype = "dashed", color = "red") +
  geom_hline(yintercept = 1, linetype = "dotted", color = "grey40") +
  scale_y_log10() +
  facet_wrap(~label, ncol = 2, scales = "free_y") +
  labs(
    x = "Respondents observed (G)",
    y = "Anytime-valid e-value (log scale)"
  ) +
  theme_minimal(base_size = 10) +
  theme(panel.grid.minor = element_blank(), strip.text = element_text(face = "bold"))
```

Figure \ref{fig:fig-evalues} shows the corresponding e-value trajectories.
Every one of the nine curated e-values exceeds the $1/\alpha$ rejection
threshold by the end of the sample. The number of respondents needed to first
cross that threshold varies enormously across attributes: from
`r format(G_cross_curated[[fastest_term]], big.mark=",")` for
*`r term_labels[[fastest_term]]`* up to
`r format(G_cross_curated[[slowest_term]], big.mark=",")` for
*`r term_labels[[slowest_term]]`* -- a much wider range than the camera case
study's 25-110, reflecting both weaker effects and a far larger $g^\star$
here, which shrinks early evidence more aggressively. As in the camera study,
crossing need not be permanent: `r length(nonmonotonic_curated)` of the nine
curated e-values
(*`r paste(term_labels[nonmonotonic_curated], collapse = "* and *")`*) dip
back below the threshold at least once after their first crossing. This is
expected of e-processes and is harmless under the relevant decision rule --
stop and reject the first time the threshold is crossed, rather than
requiring it to stay crossed forever.

Not shown in Figure \ref{fig:fig-evalues}, but visible in the full comparison
below: the curated nine are the *strongest* AMCE per attribute by
construction, and not every one of the `r length(all_terms)` AMCEs in this
study reaches the rejection threshold, even with the full sample.

## Fixed-$n$ interval vs. confidence sequence, at the final sample size

```{r fig-final, fig.width=7.5, fig.height=7.8, fig.cap=sprintf("Final AMCE point estimate with a conventional fixed-$n$ 95\\%% confidence interval versus the anytime-valid 95\\%% confidence sequence, for all %d AMCEs, both computed from the same final model fit ($G = %s$).", length(all_terms), format(meta$G_total, big.mark=","))}
ggplot(
  final_comparison,
  aes(x = label, y = estimate, ymin = conf.low, ymax = conf.high, color = method)
) +
  geom_hline(yintercept = 0, linetype = "dotted", color = "grey40") +
  geom_pointrange(position = position_dodge(width = 0.5), size = 0.35, linewidth = 0.5) +
  coord_flip() +
  scale_color_manual(values = c(
    "Conventional (fixed-n)" = "grey40",
    "Anytime-valid (CS)"     = "#2C7FB8"
  )) +
  labs(x = NULL, y = "AMCE estimate (95% interval)", color = NULL) +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom", panel.grid.minor = element_blank())
```

Figure \ref{fig:fig-final} makes explicit the price of anytime validity at a
single, fixed sample size: the two methods share the same point estimate
(they are computed from the same model fit), but the confidence sequence is
visibly wider than the conventional interval for every AMCE. Concretely,
both intervals exclude zero for `r n_both_sig` of the `r length(all_terms)`
AMCEs, and for none does the anytime-valid interval exclude zero while the
conventional interval does not -- consistent with the anytime-valid interval
never being narrower here. But `r n_conv_only` AMCEs
(*`r conv_only_labels_text`*) are flagged as distinguishable from zero by the
conventional fixed-$n$ interval while the anytime-valid confidence sequence
still contains zero, and a further `r n_neither_sig`
(*`r neither_labels_text`*) are indistinguishable from zero under either
method. That extra width purchased by the anytime-valid interval is exactly
what buys the ability to monitor the study continuously, as in Figures
\ref{fig:fig-cs} and \ref{fig:fig-evalues}, and still report a valid interval
or rejection decision at whatever point the analyst chooses to stop --
something the conventional interval does not license.

# Discussion

On this large, real conjoint dataset, the anytime-valid method continues to
behave exactly as the parent paper's theory predicts: confidence sequences
that are valid to inspect continuously, at the cost of extra width relative
to a conventional interval computed once at a fixed sample size. Two features
of this particular dataset are worth drawing out because they did not appear
in the smaller camera case study.

First, not every AMCE is distinguishable from zero, even with
`r format(meta$G_total, big.mark=",")` respondents. Of the
`r n_conv_only` AMCEs that the conventional interval alone flags --
`r conv_only_labels_text` -- `r length(conv_only_ever_crossed)` (namely
*`r paste(term_labels[conv_only_ever_crossed], collapse = "* and *")`*) did
cross the anytime-valid rejection threshold at some earlier point in
sequential monitoring before falling back below it by the end, illustrating
concretely why a rule that only checks significance once, at a pre-committed
$n$, is not the same rule as one that must remain valid at every $n$ an
analyst might stop at: an analyst free to stop the moment either of these
crossed would have "found" a significant effect under the conventional
logic, but that finding would not have survived to the final sample, and the
anytime-valid procedure never licenses treating it as a discovery in the
first place. `r length(conv_only_never_crossed)` more
(*`r paste(term_labels[conv_only_never_crossed], collapse = "* and *")`*)
never cross the anytime-valid threshold at all in this dataset, despite the
conventional interval excluding zero throughout. A further
`r n_neither_sig` AMCEs (*`r neither_labels_text`*) are not distinguishable
from zero under either method. All of this is a substantive as well as a
statistical observation: several country-of-origin effects (relative to the
Afghanistan baseline) and one age contrast are genuinely small and hard to
pin down even at this scale, in contrast to the uniformly large, easily
detected effects of testimony consistency, reason for migration, and
vulnerability that dominate Figure \ref{fig:fig-final}, echoing the original
Bansak et al. (2016) finding that humanitarian concerns dominate
European asylum preferences.

Second, this dataset shows what the anytime-valid math looks like at the
edge of floating-point range. With `r format(meta$G_total, big.mark=",")`
clusters and some very large effects, several e-values grow large enough to
overflow to $\infty$ in double precision well before the study ends (see
Figure \ref{fig:fig-evalues}'s caption); the underlying data preserve the
true (infinite) values, and only the figure's display is capped. This did
not arise in the smaller camera case study and is a reminder that
"e-value $=\infty$" is not a bug but the expected behavior of an e-process
once evidence for a real, large, and precisely-estimated effect becomes
overwhelming.

# References

- Bansak, K., Hainmueller, J., and Hangartner, D. (2016). How economic,
  humanitarian, and religious concerns shape European attitudes toward
  asylum seekers. *Science*, 354(6309), 217-222.
- Bansak, K., Hainmueller, J., and Hangartner, D. (2023). Europeans' support
  for refugees of varying background is stable over time. *Nature*,
  620(7975), 849-854. Replication data: Harvard Dataverse,
  doi:10.7910/DVN/FTL1MM.
- Lindon, M., Ham, D., Tingley, M., and Bojinov, I. (2026). Anytime-valid
  linear models and regression adjusted causal inference in randomized
  experiments. *Journal of the American Statistical Association*.
  arXiv:2210.08589.
- Molitor, D., Gosciak, J., and Lindon, M. (2026). Anytime-Valid Inference in
  Conjoint Experiments.
